\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-25 doc/sw-system.tex
Added some text describing offline analysis for issue #40.

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for stage 2. The sample of
subjects classified during stage 2 was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at stage 1. These were
classified for one week, with no retirement but a maximum classification
number of 50 each. {\bf The number of subjects at stage 2 was small enough that we
did not need to retire any: instead, we simply collected classifications for a
fixed period of time (about 4 weeks). Without the time pressure motivating the
online analysis, we implemented an ``offline'' version of the analysis that
performs a joint inference of all Agent confusion matrix elements and subject
probabilities simultaneously, for comparison. We describe how this differs
from the online analysis in the appendix. }

\todo{Chris}{Please check and edit the offline analysis description (in bold)
above -- and then the text in the appendix! (issue \#40)}

@@

The mathematics of the offline inference are presented elsewhere (in
preparation). Here we briefly note that we maximize the joint 
posterior probability distribution for all the model parameters (some 66,000
confusion matrix elements and 430,000 subject probabilities) with a simple
expectation-maximisation algorithm. This procedure takes [approximately the
same | somewhat less | somewhat more] CPU time as the online analysis, because
[insert reason]. Other comments about the relative performance]. The plots in
\Sref{sec:results:sample} show the difference in performance between the
online and offline analyses.

\todo{Chris}{Please check this text and edit appropriately (issue \#40)}

>>>>

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for stage 2. The sample of
subjects classified during stage 2 was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at stage 1. These were
classified for one week, with no retirement but a maximum classification
number of 50 each. The number of subjects at stage 2 was small enough that we
did not need to retire any: instead, we simply collected classifications for a
fixed period of time (about 4 weeks). Without the time pressure motivating the
online analysis, we implemented an ``offline'' version of the analysis that
performs a joint inference of all Agent confusion matrix elements and subject
probabilities simultaneously, for comparison. We describe how this differs
from the online analysis in the appendix.

@@

The mathematics of the offline inference are presented elsewhere (in
preparation). Here we briefly note that we maximize the joint posterior
probability distribution for all the model parameters (some 66,000 confusion
matrix elements and 430,000 subject probabilities) with a simple
expectation-maximisation algorithm. This procedure takes approximately the same
CPU time as the online analysis, because no matrix inversions are required in
the algorithm. The algorithm scales well and is actually faster than the online
analysis with the larger stage 1 dataset. The expectation-maximisation
algorithm is robust to initial starting parameters in, e.g., initial Agent
confusion matrix elements and Subject probabilities. The plots in
\Sref{sec:results:sample} show the difference in performance between the online
and offline analyses.
